Centers and centralizers of higher enveloping algebras of Lie algebras

### 2020-09-08 draft.tex
small changes

The Lie bracket on $\fh$ endows ${\rm Sym} (\fh [1])$ with the additional structure of a $\PP_0$-algebra. 
On linear elements this is simply the Lie bracket on $\fh$, and one extends to the full symmetric algebra by the graded Leibniz rule.

Consider our factorization model for the $\EE_n$-enveloping algebra $\bU_n(\fg) = \clieu (\fg \otimes \Omega_c)$. 
The filtration on Chevalley--Eilenberg chains equips $\bU_n(\fg)$ with a filtration as a factorization algebra.

@@

@@

\begin{dfn}
\label{dfn:constructible1}
Let $\bC_n(\fg)$ be the following constructible factorization algebra on $M \times \RR_{\geq 0}$:
\begin{itemize}
\item to an open set $U \subset M \times \RR_{> 0}$, we assign the cochain complex 
\[
\bC_n (\fg) (U) = \clies \bigg(\fg \otimes \Omega (U) \; , \; \Sym \left(\fg \otimes \Omega_c(U) [2] \right) \bigg) .
\]
\item to an open set $V \times [0,\epsilon)$ we assign the cochain complex 
\[
\bC_n (\fg) (V \times [0,\epsilon)) = {\rm Sym} \left(\fg \otimes \Omega^\bu_c (V \times [0,\epsilon) [2] \right).
\]
\end{itemize}
The structure map associated to the embedding 
\[
U \sqcup V \times [0, \epsilon) \hookrightarrow V' \times [0,\epsilon')
\]
is
\[
\clies \bigg(\fg \otimes \Omega^\bu (U) \; , \; \Sym \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \bigg) \; \otimes \;  {\rm Sym} \left(\fg \otimes \Omega^\bu_c (V\times [0,\epsilon)) [2] \right) 
\]
\brian{finish}
\end{dfn}

@@

Next, we provide a construction of a factorization pair on the manifold $M$ from that data of a constructible factorization algebra on $M \times \RR_{\geq 0}$. 
Suppose $\bA$ is any constructible factorization algebra on a manifold with boundary $M \times \RR_{\geq 0}$. 
Let $\pi : M \times \RR_{\geq 0} \to M$ be the projection and denote by $\pi|_{M \times \RR_{>0}}$ its restriction to the interior. 
Define the following two factorization algebras on $M$:
\begin{align*}
\bA^\circ & = \left(\left.\pi\right|_{M \times \RR_{>0}} \right)_* \bA \\
\bA^\partial & = \pi_* \bA
\end{align*}
It is immediate to check that $(\bA^\circ, \bA^\partial)$ form a factorization pair in the sense of Definition \ref{dfn:pair}. 
In fact, this construction determines a functor from the category of constructible factorization algebras on $M \times \RR_{\geq 0}$ to factorization pairs on $M$.

 \begin{lmm}
 \brian{fix notation}
Let $M$ be an $n$-dimensional manifold.
There is a quasi-isomorphism of  $\PP_0$-factorization algebras on $M$:
\[
\pi_* \overset{\circ}{\bf Z}_n(\fg) \; \xto{\simeq} \; {\rm Gr} \; \bZ_n(\fg) .
\]
where $\pi : M \times \RR_{>0} \to M$ is the projection. 
\end{lmm}

In fact, we will show that this quasi-isomorphism is a deformation retraction.

\begin{proof}
To exhibit this quasi-isomorphism, we introduce the following cochain maps.
For an open set $U \subset M$ let
\[
\int_\RR : \Omega_c(U \times \RR) \to \Omega_c (U) [1] 
\] 
be the map which integrates a compactly supported form on $U \times \RR$ along $\RR$. 
This map is a quasi-isomorphism for any $U $ and admits the following explicit retract. 
Let $\phi$ be a fixed compactly supported function on $\RR$ of mass $1$ and define
\[
r_\phi : \Omega_c(U) [1] \to \Omega_c (U \times \RR)
\]
by $r_\phi (\alpha) = \alpha \wedge \phi \, \d t$. 
\end{proof}

Since the universal action of $\bZ_n(\fg)$ on $\bU_n (\fg)$ is compatible with the above filtrations, we obtain the following constructible factorization algebra on $M \times \RR_{\geq 0}$.

>>>>

Consider our factorization model for the $\EE_n$-enveloping algebra $\bU_n(\fg) = \cliels (\fg \otimes \Omega^\bu_c)$. 
The filtration on Chevalley--Eilenberg chains equips $\bU_n(\fg)$ with a filtration as a factorization algebra.

@@

\begin{proof}
For any $L_\infty$ algebra $\fh$, the associated graded of the Chevalley--Eilenberg complex ${\rm Gr} \; \cliels {\rm Sym} (\fh [1])$ is equipped with the structure of a $\PP_0$-algebra.
It is given by the sum of the $L_\infty$-operations $\ell_2 + \ell_3 + \cdots$. 
This implies that ${\rm Gr} \; \bU_n (\fg)$ is a $\PP_0$-factorization algebra.

Next, recall that to an open set $U \subset M$ the factorization algebra ${\rm Gr} \; \bZ_n (\fg)$ assigns the cochain complex whose underlying 
\[
\clie^\bu\bigg(\fg \otimes \Omega^\bu (U) \; , \; {\rm Sym} \left(\fg \otimes \Omega^\bu_c(U) [1]\right) \bigg) = {\rm Hom}^\bu \bigg(\cliels(\fg \otimes \Omega^\bu(U)) , \cliels (\fg \otimes \Omega^\bu_c(U)) \bigg).
\]
\brian{how to handle homs}.
\end{proof}

@@

\begin{dfn}
\label{dfn:constructible1}
Let $\bC_n(\fg)$ be the following constructible factorization algebra on $M \times \RR_{\geq 0}$:
\begin{itemize}
\item to an open set $U \subset M \times \RR_{> 0}$, we assign the cochain complex 
\[
\bC_n (\fg) (U) = \clies \bigg(\fg \otimes \Omega (U) \; , \; \Sym \left(\fg \otimes \Omega_c(U) [2] \right) \bigg) .
\]
\item to an open set $V \times [0,\epsilon)$ we assign the cochain complex 
\[
\bC_n (\fg) (V \times [0,\epsilon)) = {\rm Sym} \left(\fg \otimes \Omega^\bu_c (V \times [0,\epsilon) [2] \right).
\]
\end{itemize}
The structure map associated to the embedding 
\begin{equation}\label{eqn:embed}
U \sqcup V \times [0, \epsilon) \hookrightarrow V' \times [0,\epsilon')
\end{equation}
is
\[
\begin{tikzcd}
\clies \bigg(\fg \otimes \Omega^\bu (U) \; , \; \Sym \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \bigg) \; \otimes \;  {\rm Sym} \left(\fg \otimes \Omega^\bu_c (V\times [0,\epsilon)) [2] \right) \ar[d] \\
\Sym \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \; \otimes \; \Sym \left(\fg \otimes \Omega^\bu_c (V \times [0,\epsilon)) [2] \right) \ar[d] \\
\Sym\left(\fg \otimes \left(\Omega^\bu_c(U) \oplus \Omega^\bu_c(V \times [0,\epsilon)) \right) [2] \right) \ar[d]\\
\Sym \left( \fg \otimes \Omega^\bu_c(V' \times [0,\epsilon')) [2] \right)
\end{tikzcd}
\]
The first map projects onto the $\Sym^0$ component of $\clie^\bu$ and the second map uses the fact that the symmetric algebra functor is monoidal. 
Finally, the third map is induced by the extension of compactly supported de Rham forms along the embedding (\ref{eqn:embed}). 
\end{dfn}

@@

Next, we provide a construction of a factorization pair on the manifold $M$ from the data of a constructible factorization algebra on $M \times \RR_{\geq 0}$. 
Suppose $\bA$ is any constructible factorization algebra on a manifold with boundary $M \times \RR_{\geq 0}$. 
Let $\pi : M \times \RR_{\geq 0} \to M$ be the projection and denote by $\pi|_{M \times \RR_{>0}}$ its restriction to the interior. 
Define the following two factorization algebras on $M$:
\begin{align*}
\bA^\circ & = \left(\left.\pi\right|_{M \times \RR_{>0}} \right)_* \bA \\
\bA^\partial & = \pi_* \bA
\end{align*}
It is immediate to check that $(\bA^\circ, \bA^\partial)$ form a factorization pair in the sense of Definition \ref{dfn:pair}. 
In fact, this construction determines a functor from the category of constructible factorization algebras on $M \times \RR_{\geq 0}$ to factorization pairs on $M$.

We are now ready to prove Proposition \ref{prp:pair}.

\begin{proof}[Proof of Proposition \ref{prp:pair}]
To exhibit this quasi-isomorphism, we introduce the following cochain maps.
For an open set $U \subset M$ let
\[
\int_\RR : \Omega_c(U \times \RR) \to \Omega_c (U) [1] 
\] 
be the map which integrates a compactly supported form on $U \times \RR$ along $\RR$. 
This map is a quasi-isomorphism for any $U $ and admits the following explicit retract. 
Let $\phi$ be a fixed compactly supported function on $\RR$ of mass $1$ and define
\[
r_\phi : \Omega_c(U) [1] \to \Omega_c (U \times \RR)
\]
by $r_\phi (\alpha) = \alpha \wedge \phi \, \d t$. 
\end{proof}
